Exploratory data analysis

### 2021-10-14 slides/data_checking.Rmd
remove setup data loading to helper script

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, dev = "svglite", message = FALSE, warning = FALSE, fig.asp = 3/4)
require(tidyverse)
require(magrittr)

demos_ids <- read_csv(here::here("ignore", "data", "demos_ids.csv"))
q_google_demos <- read_csv(here::here("ignore", "data", "q_google_demos.csv")) %>% 
  right_join(demos_ids, by = "demographics_id") %>% 
  mutate(subj_num = factor(subj_num))

j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv")) %>% 
  mutate(resp_conf = if_else(is.na(resp_recall), NA_real_, resp_conf))

j_exp <- j_recall %>% 
  group_by(subj_num) %>% 
  summarize(j_score = mean(acc_recall))

j_recall %<>%
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))

j_meta <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_states.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
         resp = fct_relevel(resp, "Learning Memory", after = Inf))
j_meta_desc <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_descriptions.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
encoding <- read_csv(here::here("ignore", "data", "task_encoding.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
         already_knew = fct_recode(already_knew,
                               none = "Did not know this before",
                               some = "Knew some of this before",
                               all = "Knew all of this before"))
r_facts <- read_csv(here::here("ignore", "data",  "task_retrieval_facts.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
r_pics <- read_csv(here::here("ignore", "data", "task_retrieval_pics.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
r_source <- read_csv(here::here("ignore", "data", "task_retrieval_source.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
q_trivia_demos  <- read_csv(here::here("ignore", "data", "q_trivia_demos.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))

q_posttask  <- read_csv(here::here("ignore", "data", "q_posttask.csv"))

retrieval <- r_facts %>%
  select(subj_num, j_score, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_start_recall = rt_start, rt_end_recall = rt_end) %>% 
  left_join(r_pics %>% 
              select(subj_num, group, group_trial_num, category, resp_pic = resp, rt_pic = rt)) %>% 
  left_join(r_source %>%
              select(subj_num, group, group_trial_num, category, resp_source = resp, rt_source = rt)) %>%
  left_join(encoding %>% 
              select(subj_num, group, group_trial_num, category, interest = resp, already_knew)) %>% 
  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
                                          retrieval_block <= 8 ~ "ep_same_sem_diff",
                                          retrieval_block <= 12 ~ "ep_diff_sem_same",
                                          retrieval_block <= 16 ~ "ep_diff_sem_diff",
                                          TRUE ~ NA_character_),
         encoding_trial_num = if_else(group == "academic",
                                      group_trial_num * 2 - 1,
                                      group_trial_num * 2))
```

@@

```{r}
j_exp %>% 
  ggplot(aes(x = j_score)) +
  geom_histogram() +
  geom_vline(xintercept = 0.7, linetype = "dotted")
```

@@

@@

@@

### Better experts tend to be more confident

This effect does not necessarily imply that better experts are _overconfident._ Rather, it is consistent with better experts tending to have higher latent knowledge for each question, and thus being likely to be more confident overall, even when the answer turns out to be wrong.

```{r}
j_recall %>% 
  group_by(subj_num, j_score) %>% 
  summarize(conf_q500 = median(resp_conf, na.rm = TRUE),
            conf_q250 = quantile(resp_conf, .25, na.rm = TRUE),
            conf_q750 = quantile(resp_conf, .75, na.rm = TRUE),
            conf_q025 = quantile(resp_conf, .025, na.rm = TRUE),
            conf_q975 = quantile(resp_conf, .975, na.rm = TRUE)) %>% 
  ggplot(aes(x = subj_num, y = conf_q500, color = j_score)) +
  # geom_errorbar(aes(ymin = conf_q025, ymax = conf_q975), width = 0, size = 0.5) +
  geom_errorbar(aes(ymin = conf_q250, ymax = conf_q750), width = 0, size = 1) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_viridis_c() +
  theme_bw() +
  theme(axis.text.y = element_blank())
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      dev = "svglite",
                      message = FALSE,
                      warning = FALSE,
                      fig.asp = 3/4)

source(here::here("R", "get_cleaned_data.R"))
```

@@

```{r}
j_exp %>% 
  ggplot(aes(x = j_score)) +
  geom_histogram(binwidth = .05) +
  geom_vline(xintercept = 0.7, linetype = "dotted")
```

### Are men and women participants balanced on trivia expertise?

```{r}
j_exp %>% 
  mutate(subj_num = factor(subj_num)) %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  ggplot(aes(x = j_score, fill = gender)) +
  geom_histogram(binwidth = .05, position = "identity", alpha = 0.5) +
  geom_vline(xintercept = 0.7, linetype = "dotted")
```

### Do older participants know more trivia?

```{r}
j_exp %>% 
  mutate(subj_num = factor(subj_num)) %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  ggplot(aes(x = age, y = j_score)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.7, linetype = "dotted")
```

@@

```{r}
j_recall %>% 
  mutate(resp_conf = coalesce(resp_conf, 0), 
         resp_conf_bin = cut_interval(resp_conf, length = 25, labels = FALSE)) %>% 
  group_by(subj_num, j_score, resp_conf_bin) %>% 
  summarize(acc = mean(acc_recall), n_trials = n()) %>% 
  ggplot(aes(x = resp_conf_bin, y = acc, color = j_score)) + 
  geom_line(aes(group = subj_num), alpha = 0.5) + 
  geom_point(aes(size = n_trials), alpha = 0.5) + 
  scale_color_viridis_c()
```

@@

I still haven't sorted out the best way to think about this, or how important it really is, we see a vaguely Dunning-Krugery effect where participants with lower overall scores tend to be more wrong at higher confidence.

@@
